Reproducible Validation and Replication Studies in Nanoscale Physics

### 2020-07-25 tex/results.tex
work on repro section

 Barba (2019) describes the elements of reproducible computational research that we have adopted in our practice \cite{barba2019praxis}. 
 A key element is professional software management and engineering, and the central technology solution is version control. 
 Preserving a complete history of changes is the only way to manage complex software projects that can support reproducibility.
Our signature reproducibility practice is to organize and share in an archival-quality repository (providing a global identifier) all digital artifacts associated with the results in the paper. 
This includes input files, configuration files, post-processing scripts, files specifying the build process and containerization (e.g., Docker files), and even cloud computing machine definitions, if applicable \citep{mesnard-barba2019}.
We call these openly shared file sets \emph{reproducibility packages}, or repro-packs for short.

>>>>

 Barba (2019) describes the elements of reproducible computational research that we have adopted in our practice \cite{barba2019praxis}. 
 A key element is professional software management and engineering, and the central technology solution is version control. 
 Preserving a complete history of changes is the only way to manage complex software projects that can support reproducibility.
 Another key element of transparent and reproducible computational modeling is \emph{automation}.
Automating every step means \emph{turning protocols into code.}
For example, simulations are launched with parameters fed from a configuration file rather than an interactive prompt, and all figures and plots are produced by writing scripts, rather than pointing-and-clicking on a graphical interface. 
The goal is to create complete ``recipes'' in code, which can be run, versioned, and shared.

Our signature reproducibility practice is to organize and share in an archival-quality repository (providing a global identifier) all digital artifacts associated with the results in the paper. 
This includes input files, configuration files, post-processing scripts, files specifying the build process and containerization (e.g., Docker files), and even cloud computing machine definitions, if applicable \cite{mesnard-barba2019}.
We call these openly shared file sets \emph{reproducibility packages}, or repro-packs for short.
